---
title: "Lopez_ECON691_Lab07"
author: "Brian Lopez"
date: "11/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
```

## Lab 07

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
library(plyr)
library(dplyr)
library(reshape2)
library(ggplot2)
library(textclean)
library(tm)
library(maps)
library(textstem)
library(Rcpp)
library(text2vec)
library(tidytext)
library(widyr)
library(irlba)
library(Matrix)
library(stm)
library(caret)
library(e1071)
library(LiblineaR)
library(naivebayes)
library(caTools)
```

```{r, message=FALSE, warning=FALSE}
# Load NLP environment
load_NLP_env <- function(func_dir){
  
  set.seed(1234567890)
  
  options(stringsAsFactors = F)
  
  packages <- c(
    "plyr",
    "dplyr",
    "reshape2",
    "ggplot2",
    "textclean",
    "tm",
    "maps",
    "Rcpp",
    "text2vec",
    "tidytext",
    "widyr",
    "irlba",
    "Matrix",
    "stm",
    "textstem"
  )
  
  # install packages if they don't exist
  new_packages <- packages[!(packages %in% installed.packages()[,"Package"])]
  if(length(new_packages)) {install.packages(new_packages)}
  
  # load packages
  sapply(packages, library, character.only = TRUE)
  
  print(paste("packages loaded: ", paste(packages, collapse = ", ")))
  
  # load functions library
  for (i in list.files(func_dir, pattern = "\\.[RrSsQq]$", recursive = TRUE)) {
    source(file.path(func_dir, i))
  }
  
  print(paste("functions loaded: ", paste(unlist(list.files(func_dir, pattern = "\\.[RrSsQq]$", recursive = TRUE)),
                                    collapse = ", ")))
}
```

```{r, message=FALSE, warning=FALSE}
# Load Preprocessing function
pre_process_corpus <- function(data, text_col, remove_html = TRUE, replace_emojis = FALSE, replace_numbers = FALSE,
                               replace_strings = NULL, remove_strings = NULL, non_stopwords = NULL,
                               extra_stopwords = NULL, root_gen = NULL, output_corpus = FALSE){
  
  text <- data[, text_col]
  
  # remove html encoding
  if(remove_html == T){
    text <- gsub("&gt;|&lt;"," ", text, perl = TRUE)
    text <- gsub("<[^>]*>", " ", text, perl = TRUE)
  }
  
  # remove hex encoding
  if(remove_html == T){
    text <- gsub("[\x80-\xff]", " ", text)
    text <- gsub("&quot;|&#x2F;", " ", text, perl = TRUE)
    text <- gsub("&#x2F;","/", text, perl = TRUE)
  }
  
  # replacing contractions
  text <- replace_contraction(text)
  
  # replace emojis
  if(replace_emojis == T){
    text <- replace_emoji(text)
  }
  
  # replace numbers
  if(replace_numbers == T){
    text <- replace_number(text)
  }
  
  # converting all text to lower case
  text <- tolower(text)
  
  # removing non-ascii characters
  text <- gsub("[^\001-\177]",'', text, perl = TRUE)
  
  # replace specific strings
  if(!is.null(replace_strings)){
    old_str <- replace_strings[1:(length(replace_strings)/2)]
    new_str <- replace_strings[((length(replace_strings)/2) +1):length(replace_strings)]
    for(i in 1:length(old_str)){text <- gsub(old_str[i], new_str[i], text)}
  }
  
  # removing specific strings
  if(!is.null(remove_strings)){
    strs <- paste(remove_strings, collapse = "|")
    
    text <- strsplit(text, " ")
    text <- unlist(lapply(text, function(x) {
      paste(x[!grepl(strs, x)], collapse = " ")
    }))
  }
  
  # converting to volatile corpus
  text <- VCorpus(VectorSource(text))
  
  # removing terms from stopword dictionary
  stopwords <- stopwords()
  stopwords <- stopwords[which(!stopwords %in% non_stopwords)]
  
  # adding stopwords
  stopwords <- c(stopwords,extra_stopwords)
  
  # removing stopwords
  text <- tm_map(text, function(x) {removeWords(x,stopwords)})
  
  # removing punctuation, numbers, and whitespace
  text <- tm_map(text, function(x) {removePunctuation(x)})
  text <- tm_map(text, function(x) {removeNumbers(x)})
  text <- tm_map(text, function(x) {stripWhitespace(x)})
  
  # generating term roots
  if(!is.null(root_gen)){
    if(root_gen == 'stem'){
      text <- ldply(lapply(text, function(x) {stem_strings(x$content)}), rbind)[, 2]
      text <- VCorpus(VectorSource(text))
    }
    
    if(root_gen == 'lemmatize'){
      text <- ldply(lapply(text, function(x) {lemmatize_strings(x$content)}), rbind)[, 2]
      text <- VCorpus(VectorSource(text))
    }
  }
  
  if(output_corpus == TRUE){
   return(text)
  } else {return(unlist(lapply(text, function(x){x$content})))}
  
}
```

```{r, message=FALSE, warning=FALSE}
# Load data 
enron <- read.csv('C:/Users/bjlop/Downloads/enron_emails_labeled.csv')
colnames(enron)
```

```{r, message=FALSE, warning=FALSE}
# Preprocess text
text <- pre_process_corpus(enron, "body", root_gen = 'lemmatize')

enron$body_preprocessed <- text
```

```{r, message=FALSE, warning=FALSE}
# Create train/test sets
rand <- runif(nrow(enron))
sets <- ifelse(rand < 0.9, 'train', 'test')
enron$set <- sets 

train <- enron[enron$set == 'train',]

# Tokenize and create vocabulary
it_train <- itoken(train$body_preprocessed,
                   tokenizer = word_tokenizer, ids = train$email_id)
vocab <- create_vocabulary(it_train, ngram = c(1, 3))

lbound <- round(0.009 * nrow(train))
ubound <- nrow(train) - lbound

vocab <- vocab[vocab$doc_count > lbound & vocab$doc_count < ubound,]

vectorizer <- vocab_vectorizer(vocab)
dtm_train <- create_dtm(it_train, vectorizer)

test <- enron[enron$set == 'test',]
it_test <- itoken(test$body_preprocessed,
                   tokenizer = word_tokenizer, ids = test$email_id)

dtm_test <- create_dtm(it_test, vectorizer)
```

```{r, message=FALSE, warning=FALSE}
# Model
library(caret)
```

```{r, message=FALSE, warning=FALSE}
# Tune model for custom f beta function
calc_f5 <- function(data, lev = NULL, model = NULL){
  recall <- nrow(data[data[, "obs"] == 1 & data[, "pred"] == 1,])/
    nrow(data[data[, "obs"] == 1,])
  precision <- nrow(data[data[, "obs"] == 1 & data[, "pred"] == 1,])/
    nrow(data[data[, "pred"] == 1,])
  out <- (1 + 5^2)*(precision * recall)/((5^2 * precision) + recall)
  names(out) <- 'f5'
  out
}

trctrl <- trainControl(method = "repeatedcv", number = 3, repeats = 3, summaryFunction = calc_f5)
```

```{r, message=FALSE, warning=FALSE}
#expand.grid(cost=c(0, 0.5, 1), Loss = c(0, 1), weight = c(0,1))
```

```{r, message=FALSE, warning=FALSE}
library(LiblineaR)

enron_svm <- train(x = as.matrix(dtm_train),
                 y = as.factor(train$company_business),
                 method = "svmLinearWeights2",
                 trControl = trctrl,
                 tuneGrid = data.frame(cost = 1, Loss = 0, weight = 1))

pred_test <- predict(enron_svm, as.matrix(dtm_test))

preds <- data.frame(id = enron$email_id[enron$set == "test"], 
                    label = enron$company_business[enron$set == "test"],
                    svm = as.numeric(as.character(pred_test)))

f5_svm <- calc_fbeta(preds, "label", 1, "svm", 1, 5)
f5_svm

table(preds$label, preds$svm)
```

```{r, message=FALSE, warning=FALSE}
# Naive-Bayes
library(naivebayes)

model_nb <- train(x = as.matrix(dtm_train),
                y = as.factor(train$company_business),
                method = "naive_bayes",
                trControl = trctrl,
                tuneGrid = data.frame(laplace = 0, usekernel = FALSE, adjust = FALSE))

pred_test <- predict(model_nb, as.matrix(dtm_test))

preds$nb <- as.numeric(as.character(pred_test))

f5_nb <- calc_fbeta(preds, "label", 1, "nb", 1, 5)
f5_nb

table(preds$label, preds$nb)
```

```{r, message=FALSE, warning=FALSE}
# Random Forest
library(caTools)

model_rf <- train(as.matrix(dtm_train),
            y = as.factor(train$company_business),
            method = "ranger",
            trControl = trctrl,
            tuneGrid = data.frame(mtry = floor(sqrt(dim(as.matrix(dtm_train))[2])),
                            splitrule = "gini",
                            min.node.size = 1))

pred_test <- predict(model_rf, as.matrix(dtm_test))

preds$rf <- as.numeric(as.character(pred_test))

f5_rf <- calc_fbeta(preds, "label", 1, "rf", 1, 5)
f5_rf
```

The random forest by far perfomed the best among our support vector machine (svm) model, naive-bayes model, and random forest model. This is while optimizing for f score, meaning we are prioritizing the correct labeling of true negatives rather than true positives. For this specific case, we are much more concerned with false negatives (ie, mistakenly discarding a document that should have been kept) than false positives (keeping a document that should not have been kept). Therefore, the model’s performance would be better evaluated with a metric that values recall significantly more than precision. Using my best model (Random Forest), my estimated error cost per 100 dosuments is 4,000 dollars.

Note: The company estimates that a document that should have been stored but was discarded costs them 200 dollars in lost potential value, and a document that should have been discarded but was stored costs 40 dollars in administration, storage, and review.


